---
title: "Project 2"
author: "Huizenga"
date: '`r Sys.Date()`'
output: html_document
---

```{r}
library(broom)
library(ggplot2)
library(dplyr)
library(plm)
library(patchwork)
library(grid)
library(cowplot)
library(ggtext)
library(knitr)
library(flextable)
library(officer)
library(tidyr)
```

## Loading Data & Merging

```{r}
leg <- read.csv("/Users/emmahuizenga/Desktop/IPPSR/Project 2/working files/data/Gender Comp in State Leg.xlsx - Legislature Data.csv")

policy <- read.csv("/Users/emmahuizenga/Desktop/IPPSR/Project 2/working files/data/(Shortened) CSPP_ State-Level Mandated Insurance Coverage - policy.csv") %>% 
  select(-"any_policy")
```

```{r}
gems <- left_join(leg, policy, by = c("state", "year"))
```

## Unadjusted Model Women, positve grouping

```{r}
dependent_variables_women = c("pos_women", "abor_man", "fer_treat", "contra_all", "contra_script", "contra_otc_script", "contra_otc_wo_script", "contra_ex_sup", "contra_no_share")
```

```{r}
models_women <- list()

for (dv in dependent_variables_women) {
  formula <- as.formula(paste(dv, "~ prop_leg_women")) #creating formula (dv ~ treatment) to insert into plm
  model <- plm(formula, data = gems, index = c("state", "year")) #running model with all dvs, saving it in "model"
  models_women[[dv]] <- model #saving all models in empty list models_women with 
}

models_women

tidy_models_women <- bind_rows(                             # combining all model outputs into one data frame
  lapply(names(models_women), function(dv) {                # loop over the names of the models (each name is a dependent variable)
    tidy(models_women[[dv]], conf.int = TRUE) %>%   # tidy the model output and include confidence intervals
      mutate(dependent_variable = dv)                      # adding a column for the dependent variable name
  }), 
  .id = "model"                                             # adding a column named 'model' to identify the source model for each row
)

tidy_models_women
```

## Unadjusted Model Men, positive grouping

```{r}
dependent_variables_men = c("pos_men", "pros_scr", "er_dys_man", "vase")
```

```{r}
models_men <- list()

for (dv in dependent_variables_men) {
  formula <- as.formula(paste(dv, "~ prop_leg_women"))
  model <- plm(formula, data = gems, index = c("state", "year"))
  models_men[[dv]] <- model
}

models_men

tidy_models_men <- bind_rows(lapply(names(models_men), function(dv) {
  tidy(models_men[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

tidy_models_men
```

## Unadjusted Model Trans, positive grouping

```{r}
dependent_variables_trans = c("pos_trans", "gen_affirm_man", "horm_ther")
```

```{r}
models_trans <- list()

for (dv in dependent_variables_trans) {
  formula <- as.formula(paste(dv, "~ prop_leg_women"))
  model <- plm(formula, data = gems, index = c("state", "year"))
  models_trans[[dv]] <- model
}

models_trans

tidy_models_trans <- bind_rows(lapply(names(models_trans), function(dv) {
  tidy(models_trans[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

tidy_models_trans
```

## Adjusted Model Women, positive grouping

```{r}
# confounders
gems$dem_prop <- gems$leg_dem_all / (gems$leg_dem_all + gems$leg_rep_all + gems$leg_thi_all)
gems$dem_leg_maj <- gems$dem_prop > 0.5
```

```{r}
models_women_part <- list()

for (dv in dependent_variables_women) {
  formula <- as.formula(paste(dv, "~ prop_leg_women + dem_prop + dem_leg_maj"))  # used to be `leg_dem_all`
  model <- plm(formula, data = gems, index = c("state", "year")) 
  models_women_part[[dv]] <- model
}

models_women_part

tidy_models_women_part <- bind_rows(                            
  lapply(names(models_women_part), function(dv) {               
    tidy(models_women_part[[dv]], conf.int = TRUE) %>%   
      mutate(dependent_variable = dv)                      
  }), 
  .id = "model"                                             
)

tidy_models_women_part
```

## Adjusted Model Men, positive grouping

```{r}
models_men_part <- list()

for (dv in dependent_variables_men) {
  formula <- as.formula(paste(dv, "~ prop_leg_women + dem_prop + dem_leg_maj"))
  model <- plm(formula, data = gems, index = c("state", "year"))
  models_men_part[[dv]] <- model
}

models_men_part

tidy_models_men_part <- bind_rows(
  lapply(names(models_men_part), function(dv) {
    tidy(models_men_part[[dv]], conf.int = TRUE) %>%
      mutate(dependent_variable = dv)  
}), .id = "model")

tidy_models_men_part
```

## Adjusted Model Trans, positive grouping

```{r}
models_trans_part <- list()

for (dv in dependent_variables_trans) {
  formula <- as.formula(paste(dv, "~ prop_leg_women + dem_prop + dem_leg_maj"))
  model <- plm(formula, data = gems, index = c("state", "year"))
  models_trans_part[[dv]] <- model
}

models_trans_part

tidy_models_trans_part <- bind_rows(
  lapply(names(models_trans_part), function(dv) {
    tidy(models_trans_part[[dv]], conf.int = TRUE) %>%
     mutate(dependent_variable = dv)  
}), .id = "model")

tidy_models_trans_part
```

## Regression W/O Fixed Effects for Women, positive grouping & controlling for partisanship

```{r}
models_women_lm <- list()

for (dv in dependent_variables_women) {
  formula <- as.formula(paste(dv, "~ prop_leg_women + dem_prop + dem_leg_maj")) 
  model <- lm(formula, data = gems) 
  models_women_lm[[dv]] <- model 
}

models_women_lm

tidy_models_women_lm <- bind_rows(lapply(names(models_women_lm), function(dv) {
  tidy(models_women_lm[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

tidy_models_women_lm
```

## Regression W/O Fixed Effects for Men, positive grouping & controlling for partisanship

```{r}
models_men_lm <- list()

for (dv in dependent_variables_men) {
  formula <- as.formula(paste(dv, "~ prop_leg_women + dem_prop + dem_leg_maj"))  
  model <- lm(formula, data = gems)  
  models_men_lm[[dv]] <- model  
}

models_men_lm

tidy_models_men_lm <- bind_rows(lapply(names(models_men_lm), function(dv) {
  tidy(models_men_lm[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

tidy_models_men_lm
```

## Regression W/O Fixed Effects for Trans, positive grouping & controlling for partisanship

```{r}
models_trans_lm <- list()

for (dv in dependent_variables_trans) {
  formula <- as.formula(paste(dv, "~ prop_leg_women + dem_prop + dem_leg_maj" ))  
  model <- lm(formula, data = gems)  
  models_trans_lm[[dv]] <- model  
}

models_trans_lm

tidy_models_trans_lm <- bind_rows(lapply(names(models_trans_lm), function(dv) {
  tidy(models_trans_lm[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

tidy_models_trans_lm
```

## Combinding unadj., adj., & OLS models into dfs for plotting

```{r}
tidy_models_women <- tidy_models_women %>%
  mutate(model_type = "Unadjusted")

tidy_models_women_part <- tidy_models_women_part %>%
  mutate(model_type = "Adjusted")

tidy_models_women_lm <- tidy_models_women_lm %>% 
  mutate(model_type = "OLS")

df_women <- bind_rows(tidy_models_women, tidy_models_women_part, tidy_models_women_lm) %>%
  filter(term == "prop_leg_women")
```

```{r}
tidy_models_men <- tidy_models_men %>%
  mutate(model_type = "Unadjusted")

tidy_models_men_part <- tidy_models_men_part %>%
  mutate(model_type = "Adjusted")

tidy_models_men_lm <- tidy_models_men_lm %>%
  mutate(model_type = "OLS")

df_men <- bind_rows(tidy_models_men, tidy_models_men_part, tidy_models_men_lm) %>%
  filter(term == "prop_leg_women")
```

```{r}
tidy_models_trans <- tidy_models_trans %>%
  mutate(model_type = "Unadjusted")

tidy_models_trans_part <- tidy_models_trans_part %>%
  mutate(model_type = "Adjusted")

tidy_models_trans_lm <- tidy_models_trans_lm %>%
  mutate(model_type = "OLS")

df_trans <- bind_rows(tidy_models_trans, tidy_models_trans_part, tidy_models_trans_lm) %>%
  filter(term == "prop_leg_women")
```

## Visualization Women

```{r}
df_women$dependent_variable <- factor(
  df_women$dependent_variable,
  levels = rev(dependent_variables_women) 
)

df_women$model_type <- factor(df_women$model_type, levels = c("OLS", "Adjusted", "Unadjusted"))

df_women$dependent_variable <- forcats::fct_recode(
  df_women$dependent_variable,
  "**Women Agg.**" = "pos_women",
  "Fertility Treat. Mandate" = "fer_treat", 
  "Abortion Cov. Mandate" = "abor_man", 
  "**Contraceptives Agg.**" = "contra_all",
  "Rx Contraceptives" = "contra_script", 
  "OTC Contra. w/ Rx" = "contra_otc_script", 
  "OTC Contra. w/o Rx" = "contra_otc_wo_script", 
  "Extended Supply Contra." = "contra_ex_sup", 
  "No Cost-Sharing Contra." = "contra_no_share"
)

p1 <- ggplot(data = df_women, aes(x = estimate, y = dependent_variable, color = model_type)) +
  geom_point(position = position_dodge(width = 0.5), size = 1.5) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                position = position_dodge(width = 0.5), width = 0.2) +
  annotate("rect", xmin = -.25, xmax = 1.4, ymin = .75, ymax = 9.25, 
           fill = "grey", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") + 
  labs(x = expression(tau ~ "(" * "Average Treatment Effect" * ")"),
       y = "Women-Friendly Policies") +
       #title = "ATEs on Women-Friendly Policy Outcomes",
       #subtitle = "Fig. 2.1") +
  theme_cowplot() +
  theme(axis.text.y = ggtext::element_markdown()) +
  scale_color_manual(values = c(
  "Unadjusted" = "#ef97b7",  
  "Adjusted" = "#e13b77", 
  "OLS" = "grey30")) +
  theme(
    legend.position = c(0.69, 0.13),
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
    legend.title = element_blank()
  ) + 
  guides(color = guide_legend(
    override.order = TRUE,
    reverse = TRUE  # flips the legend order
  )) +
   theme(plot.title.position = "plot",
         plot.title = element_text(hjust = .5),        
         plot.subtitle = element_text(face = "bold",
                                      size = 15)) 

p1

ggsave("women_1.pdf", p1, width = 8, height = 5)
```

## Visualization Men

```{r}
df_men$dependent_variable <- factor(
  df_men$dependent_variable,
  levels = rev(dependent_variables_men) 
)

df_men$model_type <- factor(df_men$model_type, levels = c("OLS", "Adjusted", "Unadjusted"))

df_men$dependent_variable <- forcats::fct_recode(
  df_men$dependent_variable,
  "Erectile Dysfunction Cov." = "er_dys_man", 
  "PCa Screening" = "pros_scr", 
  "**Men Agg.**" = "pos_men",
  "Vasectomies" = "vase"
)

p2 <- ggplot(data = df_men, aes(x = estimate, y = dependent_variable, color = model_type)) +
  geom_point(position = position_dodge(width = 0.5), size = 1.5) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                position = position_dodge(width = 0.5), width = 0.2) +
  annotate("rect", xmin = -.325, xmax = .65, ymin = .55 , ymax = 4.5, 
           fill = "gray", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") + 
  labs(x = expression(tau ~ "(" * "Average Treatment Effect" * ")"),
       y = "Men-Friendly Policies")+
       #title = "ATEs on Men-Friendly Policy Outcomes",
      # subtitle = "Fig. 3.1") +
  theme_cowplot() +
  theme(axis.text.y = ggtext::element_markdown()) +
  scale_color_manual(values = c(
  "Unadjusted" = "#a59eef",  
  "Adjusted"   = "#4d3df1",
  "OLS" = "grey30")) +
  theme(
    legend.position = c(0.7, 0.14), 
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
    legend.title = element_blank(),
    plot.title.position = "plot",
    plot.title = element_text(hjust = .5),        
    plot.subtitle = element_text(face = "bold",
                                      size = 15)) +
  guides(color = guide_legend(
    override.order = TRUE,
    reverse = TRUE  
  ))

p2

ggsave("men_1.pdf", p2, width = 8, height = 5)
```

## Visualization Trans

```{r}
df_trans$dependent_variable <- factor(
  df_trans$dependent_variable,
  levels = rev(dependent_variables_trans) 
)

df_trans$model_type <- factor(df_trans$model_type, levels = c("OLS", "Adjusted", "Unadjusted"))

df_trans$dependent_variable <- forcats::fct_recode(
  df_trans$dependent_variable,
  "**Trans Agg.**" = "pos_trans",
  "Gender Affirming Care" = "gen_affirm_man", 
  "Hormone Therapy" = "horm_ther", 
)

p3 <- ggplot(data = df_trans, aes(x = estimate, y = dependent_variable, color = model_type)) +
  geom_point(position = position_dodge(width = 0.5), size = 1.5) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                position = position_dodge(width = 0.5), width = 0.2) +
  annotate("rect", xmin = -.05, xmax = .75, ymin = .55, ymax = 3.5, 
           fill = "gray", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") + 
  labs(x = expression(tau ~ "(" * "Average Treatment Effect" * ")"),
       y = "Trans-Friendly Policies") +
      # title = "ATEs on Trans-Friendly Policy Outcomes",
      # subtitle = "Fig. 4.1") +
  theme_cowplot() +
  theme(axis.text.y = ggtext::element_markdown()) +
  scale_color_manual(values = c(
  "Unadjusted" = "#b88ec9",  
  "Adjusted"   = "#A442ca", 
  "OLS" = "grey30")) +
  theme(
    legend.position = c(0.69, 0.14),  
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
    legend.title = element_blank(), 
    plot.title.position = "plot",
    plot.title = element_text(hjust = .5),        
    plot.subtitle = element_text(face = "bold",
                                      size = 15)) +
  guides(color = guide_legend(
    override.order = TRUE,
    reverse = TRUE  
  ))

p3

ggsave("trans_1.pdf", p3, width = 8, height = 5)
```

## Negative grouping using all 3 models

```{r}
dependent_variables_negative = c("neg_women", "neg_men", "neg_trans", "neg_minor", "neg_all")
```

# Unadjusted model

```{r}
models_neg_unadj <- list()

for (dv in dependent_variables_negative) {
  formula <- as.formula(paste(dv, "~ prop_leg_women"))
  model <- plm(formula, data = gems, index = c("state", "year"))
  models_neg_unadj[[dv]] <- model
}

print(models_neg_unadj)

tidy_models_neg_unadj <- bind_rows(lapply(names(models_neg_unadj), function(dv) {
  tidy(models_neg_unadj[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

print(tidy_models_neg_unadj)
```

# Adjusted model

```{r}
models_neg <- list()

for (dv in dependent_variables_negative) {
  formula <- as.formula(paste(dv, "~ prop_leg_women + dem_prop + dem_leg_maj"))
  model <- plm(formula, data = gems, index = c("state", "year"))
  models_neg[[dv]] <- model
}

print(models_neg)

tidy_models_neg <- bind_rows(lapply(names(models_neg), function(dv) {
  tidy(models_neg[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

print(tidy_models_neg)
```

# OLS model

```{r}
models_neg_ols <- list()

for (dv in dependent_variables_negative) {
  formula <- as.formula(paste(dv, "~ prop_leg_women"))
  model <- lm(formula, data = gems, index = c("state", "year"))
  models_neg_ols[[dv]] <- model
}

print(models_neg_ols)

tidy_models_neg_ols <- bind_rows(lapply(names(models_neg_ols), function(dv) {
  tidy(models_neg_ols[[dv]], conf.int = TRUE) %>%
    mutate(dependent_variable = dv)  
}), .id = "model")

print(tidy_models_neg_ols)
```

## Visualization for Neg. Policies

```{r}
tidy_models_neg_unadj <- tidy_models_neg_unadj %>%
  mutate(model_type = "Unadjusted")

tidy_models_neg <- tidy_models_neg %>%
  mutate(model_type = "Adjusted")

tidy_models_neg_ols <- tidy_models_neg_ols %>%
  mutate(model_type = "OLS")

df_neg <- bind_rows(tidy_models_neg_unadj, tidy_models_neg, tidy_models_neg_ols) %>%
  filter(term == "prop_leg_women")
```

```{r}
df_neg$dependent_variable <- factor(
  df_neg$dependent_variable,
  levels = rev(dependent_variables_negative) 
)

df_neg$model_type <- factor(df_neg$model_type, levels = c("OLS", "Adjusted", "Unadjusted"))

df_neg$dependent_variable <- forcats::fct_recode(
  df_neg$dependent_variable,
  "Abortion" = "neg_women",
  "Erectile Dysfunction" = "neg_men", 
  "Gender Affirming Care" = "neg_trans", 
  "Negative Policies for Minorities" = "neg_minor",
  "All Negative Policies" = "neg_all"
)

neg <- ggplot(data = df_neg, aes(x = estimate, y = dependent_variable, color = model_type)) +
  annotate("rect", xmin = -.75, xmax = .38, ymin = .6, ymax = 5.5, 
           fill = "grey", alpha = 0.2) +
  geom_point(position = position_dodge(width = 0.5), size = 1.5) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                position = position_dodge(width = 0.5), width = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") + 
  labs(x = expression(tau ~ "(" * "Average Treatment Effect" * ")"),
       y = "Limitation Policies",
       title = "ATEs on Limitation Policy Outcomes",
       subtitle = "Fig. 7") +
  theme_cowplot() +
  theme(axis.text.y = ggtext::element_markdown()) +
  scale_color_manual(values = c(
  "Unadjusted" = "#FF745C",  
  "Adjusted" = "#9D0606", 
  "OLS" = "grey30")) +
  theme(axis.text.y = ggtext::element_markdown(),
        plot.title.position = "plot",
        legend.position = c(0.69, 0.13),
        legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
        plot.title = element_text(hjust = .5),        
        plot.subtitle = element_text(face = "bold",
                                      size = 15),
        legend.title = element_blank()) +
  guides(color = guide_legend(
    override.order = TRUE,
    reverse = TRUE))

ggsave("neg.png", neg, width = 8, height = 5)

neg
```

## Plotting unadj., adj., and ols regressions for aggregated women-friendly policy

```{r}
model_adj <- models_women_part[["pos_women"]]
model_unadj <- models_women[["pos_women"]]
model_ols <- models_women_lm[["pos_women"]]

coefs_adj <- tidy(model_adj, conf.int = TRUE)
coefs_unadj <- tidy(model_unadj, conf.int = TRUE)
coefs_ols <- tidy(model_ols, conf.int = TRUE)

tau_adj <- coefs_adj %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_adj <- coefs_adj %>% filter(term == "dem_prop") %>% pull(estimate)

tau_unadj <- coefs_unadj %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_unadj <- 0

tau_ols <- coefs_ols %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_ols <- coefs_ols %>% filter(term == "dem_prop") %>% pull(estimate)
```

```{r}
new_data <- tibble(
  prop_leg_women = seq(0, 1, by = 0.01),
  dem_prop = mean(gems$dem_prop, na.rm = TRUE)
)

new_data <- new_data %>%
  mutate(
    predicted_unadj = tau_unadj * prop_leg_women + beta1_unadj * dem_prop,
    predicted_adj = tau_adj * prop_leg_women + beta1_adj * dem_prop,
    predicted_ols = tau_ols * prop_leg_women + beta1_ols * dem_prop
)
```

```{r}
new_data_long <- new_data %>%
  pivot_longer(
    cols = starts_with("predicted_"),
    names_to = "model",
    values_to = "predicted"
  )
```

```{r}
new_data_long$model <- factor(new_data_long$model, 
                              levels = c("predicted_unadj", "predicted_adj", "predicted_ols"))

predict_women <- ggplot(new_data_long, aes(x = prop_leg_women, y = predicted, color = model)) +
  geom_line() +
  annotate("rect", xmin = 0, xmax = 1, ymin = -.05, ymax = 1, 
           fill = "grey", alpha = 0.2) +
  scale_color_manual(values = c(
    "predicted_unadj" = "#ef97b7", 
    "predicted_adj" = "#e13b77", 
    "predicted_ols" = "grey30"
  ),
  labels = c(
    "predicted_unadj" = "Unadjusted", 
    "predicted_adj" = "Adjusted", 
    "predicted_ols" = "OLS"
  )) +
  labs(
    x = "Proportion of Women in Legislature",
    y = "Probability of Policy Being Enacted",
   # subtitle = "Fig. 2.2",
   # title = "Estimated Effect of Women’s Representation on Women-Friendly Policy",
    caption  = "NOTE: Displays aggregated variable treatment effects only",
    color = "Model Type"
  ) +
  theme_cowplot() +
  theme(legend.position = c(0.76, 0.15),  
        legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
        legend.title = element_blank(), 
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position =  "plot",
        plot.title = element_text(hjust = .5),        
        plot.subtitle = element_text(face = "bold",
                                      size = 15)) 

predict_women

ggsave("predict_women_paper.pdf", predict_women, width = 8, height = 5)
```

## Plotting unadj., adj., and ols regressions for aggregated men-friendly policy

```{r}
model_adj <- models_men_part[["pos_men"]]
model_unadj <- models_men[["pos_men"]]
model_ols <- models_men_lm[["pos_men"]]

coefs_adj <- tidy(model_adj, conf.int = TRUE)
coefs_unadj <- tidy(model_unadj, conf.int = TRUE)
coefs_ols <- tidy(model_ols, conf.int = TRUE)

tau_adj <- coefs_adj %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_adj <- coefs_adj %>% filter(term == "dem_prop") %>% pull(estimate)

tau_unadj <- coefs_unadj %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_unadj <- 0

tau_ols <- coefs_ols %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_ols <- coefs_ols %>% filter(term == "dem_prop") %>% pull(estimate)
```

```{r}
new_data <- tibble(
  prop_leg_women = seq(0, 1, by = 0.01),
  dem_prop = mean(gems$dem_prop, na.rm = TRUE)
)

new_data <- new_data %>%
  mutate(
    predicted_unadj = tau_unadj * prop_leg_women + beta1_unadj * dem_prop,
    predicted_adj = tau_adj * prop_leg_women + beta1_adj * dem_prop,
    predicted_ols = tau_ols * prop_leg_women + beta1_ols * dem_prop
)
```

```{r}
new_data_long <- new_data %>%
  pivot_longer(
    cols = starts_with("predicted_"),
    names_to = "model",
    values_to = "predicted"
  )
```

```{r}
new_data_long$model <- factor(new_data_long$model, 
                              levels = c("predicted_unadj", "predicted_adj", "predicted_ols"))

predict_men <- ggplot(new_data_long, aes(x = prop_leg_women, y = predicted, color = model)) +
  geom_line() +
  annotate("rect", xmin = 0, xmax = 1, ymin = -.1, ymax = .31, 
           fill = "grey", alpha = 0.2) +
  scale_color_manual(values = c(
    "predicted_unadj" = "#a59eef", 
    "predicted_adj" = "#4d3df1", 
    "predicted_ols" = "grey30"
  ),
  labels = c(
    "predicted_unadj" = "Unadjusted", 
    "predicted_adj" = "Adjusted", 
    "predicted_ols" = "OLS"
  )) +
  labs(
    x = "Proportion of Women in Legislature",
    y = "Probability of Policy Being Enacted",
   # subtitle = "Fig. 3.2",
   # title = "Estimated Effect of Women’s Representation on Men-Friendly Policy",
    caption  = "NOTE: Displays aggregated variable treatment effects only",
    color = "Model Type"
  ) +
  theme_cowplot() +
  theme(legend.position = c(0.76, 0.15),
        legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
        legend.title = element_blank(), 
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position =  "plot",
        plot.title = element_text(hjust = .5),        
        plot.subtitle = element_text(face = "bold",
                                      size = 15)) 

ggsave("predict_men_paper.pdf", predict_men, width = 8, height = 5)
```

## Plotting unadj., adj., and ols regressions for aggregated trans-friendly policy

```{r}
model_adj <- models_trans_part[["pos_trans"]]
model_unadj <- models_trans[["pos_trans"]]
model_ols <- models_trans_lm[["pos_trans"]]

coefs_adj <- tidy(model_adj, conf.int = TRUE)
coefs_unadj <- tidy(model_unadj, conf.int = TRUE)
coefs_ols <- tidy(model_ols, conf.int = TRUE)

tau_adj <- coefs_adj %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_adj <- coefs_adj %>% filter(term == "dem_prop") %>% pull(estimate)

tau_unadj <- coefs_unadj %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_unadj <- 0

tau_ols <- coefs_ols %>% filter(term == "prop_leg_women") %>% pull(estimate)
beta1_ols <- coefs_ols %>% filter(term == "dem_prop") %>% pull(estimate)
```

```{r}
new_data <- tibble(
  prop_leg_women = seq(0, 1, by = 0.01),
  dem_prop = mean(gems$dem_prop, na.rm = TRUE)
)

new_data <- new_data %>%
  mutate(
    predicted_unadj = tau_unadj * prop_leg_women + beta1_unadj * dem_prop,
    predicted_adj = tau_adj * prop_leg_women + beta1_adj * dem_prop,
    predicted_ols = tau_ols * prop_leg_women + beta1_ols * dem_prop
)
```

```{r}
new_data_long <- new_data %>%
  pivot_longer(
    cols = starts_with("predicted_"),
    names_to = "model",
    values_to = "predicted"
  )
```

```{r}
new_data_long$model <- factor(new_data_long$model, 
                              levels = c("predicted_unadj", "predicted_adj", "predicted_ols"))

predict_trans <-ggplot(new_data_long, aes(x = prop_leg_women, y = predicted, color = model)) +
  geom_line() +
  annotate("rect", xmin = 0, xmax = 1, ymin = -.05, ymax = .5, 
           fill = "grey", alpha = 0.2) +
  scale_color_manual(values = c(
    "predicted_unadj" = "#b88ec9", 
    "predicted_adj" = "#A442ca", 
    "predicted_ols" = "grey30"
  ),
  labels = c(
    "predicted_unadj" = "Unadjusted", 
    "predicted_adj" = "Adjusted", 
    "predicted_ols" = "OLS"
  )) +
  labs(
    x = "Proportion of Women in Legislature",
    y = "Probability of Policy Being Enacted",
    #subtitle = "Fig. 4.2",
    #title = "Estimated Effect of Women’s Representation on Trans-Friendly Policy",
    caption = "NOTE: Displays aggregated variable treatment effects only",
    color = "Model Type"
  ) +
  theme_cowplot() +
  theme(legend.position = c(0.76, 0.15),
        legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
        legend.title = element_blank(), 
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position =  "plot",
        plot.title = element_text(hjust = .5),        
        plot.subtitle = element_text(face = "bold",
                                      size = 15)) 

ggsave("predict_trans_paper.pdf", predict_trans, width = 8, height = 5)
```

## MidSure Figures (ignore)

```{r}
p4 <- ggplot(data = df_women, aes(x = estimate, y = dependent_variable, color = model_type)) +
  geom_point(position = position_dodge(width = 0.5), size = 1.5) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                position = position_dodge(width = 0.5), width = 0.2) +
  annotate("rect", xmin = -.25, xmax = 1.4, ymin = .75, ymax = 9.25, 
           fill = "grey", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") + 
  labs(x = expression(tau ~ "(" * "Average Treatment Effect" * ")"),
       y = "Women-Friendly Policies") +
       #title = "Fig. 2.1") +
  theme_cowplot() +
  theme(axis.text.y = ggtext::element_markdown()) +
  scale_color_manual(values = c(
  "Unadjusted" = "#ef97b7",  
  "Adjusted" = "#e13b77", 
  "OLS" = "grey30")) +
  theme(
    legend.position = c(0.7, 0.13),
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
    legend.title = element_blank()
  ) + 
  guides(color = guide_legend(
    override.order = TRUE,
    reverse = TRUE  # flips the legend order
  )) +
   theme(plot.title.position = "plot") #NEW parameter. Apply for subtitle to

p4
```

```{r}
p5 <- ggplot(data = df_men, aes(x = estimate, y = dependent_variable, color = model_type)) +
  geom_point(position = position_dodge(width = 0.5), size = 1.5) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                position = position_dodge(width = 0.5), width = 0.2) +
  annotate("rect", xmin = -.325, xmax = .65, ymin = .55 , ymax = 4.5, 
           fill = "gray", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") + 
  labs(x = expression(tau ~ "(" * "Average Treatment Effect" * ")"),
       y = "Men-Friendly Policies") + 
       #title = "Fig. 3.1") +
  theme_cowplot() +
  theme(axis.text.y = ggtext::element_markdown()) +
  scale_color_manual(values = c(
  "Unadjusted" = "#a59eef",  
  "Adjusted"   = "#4d3df1",
  "OLS" = "grey30")) +
  theme(
    legend.position = c(0.7, 0.14), 
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
    legend.title = element_blank()) +
    #plot.title.position = "plot") +
  guides(color = guide_legend(
    override.order = TRUE,
    reverse = TRUE  
  ))

p5
```

```{r}
p6 <- ggplot(data = df_trans, aes(x = estimate, y = dependent_variable, color = model_type)) +
  geom_point(position = position_dodge(width = 0.5), size = 1.5) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                position = position_dodge(width = 0.5), width = 0.2) +
  annotate("rect", xmin = -.05, xmax = .75, ymin = .55, ymax = 3.5, 
           fill = "gray", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") + 
  labs(x = expression(tau ~ "(" * "Average Treatment Effect" * ")"),
       y = "Trans-Friendly Policies") + 
      # title = "Fig. 4.1") +
  theme_cowplot() +
  theme(axis.text.y = ggtext::element_markdown()) +
  scale_color_manual(values = c(
  "Unadjusted" = "#b88ec9",  
  "Adjusted"   = "#A442ca", 
  "OLS" = "grey30")) +
  theme(
    legend.position = c(0.69, 0.14),  
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),
    legend.title = element_blank()) + 
   # plot.title.position = "plot") +
  guides(color = guide_legend(
    override.order = TRUE,
    reverse = TRUE  
  ))

p6
```

```{r}
results_plot2 <- (p4 / p5 / p6) +
  plot_annotation(
  title = "Results", 
  tag_levels = '1', 
  tag_prefix = 'Fig. ', 
  tag_sep = '.', 
  tag_suffix = ':') &
  theme(plot.tag = element_text(size = 10))  

ggsave("results_plot_MID.png", results_plot2, width = 7, height = 10)
```

## MidSure Tables (ignore)

```{r}
save_as_image(flextable(tidy_models_women), path = "tidy_models_women.png")
save_as_image(flextable(tidy_models_men), path = "tidy_models_men.png")
save_as_image(flextable(tidy_models_trans), path = "tidy_models_trans.png")
save_as_image(flextable(tidy_models_women_part), path = "tidy_models_women_part.png")
save_as_image(flextable(tidy_models_men_part), path = "tidy_models_men_part.png")
save_as_image(flextable(tidy_models_trans_part), path = "tidy_models_trans_part.png")
save_as_image(flextable(tidy_models_neg), path = "tidy_models_neg.png")
save_as_image(flextable(tidy_models_women_lm), path = "tidy_models_women_lm.png")
save_as_image(flextable(tidy_models_men_lm), path = "tidy_models_men_lm.png")
save_as_image(flextable(tidy_models_trans_lm), path = "tidy_models_trans_lm.png")
```
